Figures

### 2018-06-28 code/figures.rmd
Increase line thickness in Figure 2 legend to make it legible

#combined line plot gives good overview. Point version of the same is also interesting.
ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type)) +
  geom_line(alpha = 0.6) +
  theme_bw() +
  scale_x_continuous(name = expression(paste("Between studies standard deviation ", tau)),
                     minor_breaks = NULL) +
  scale_y_continuous(name = expression(paste(I^2," index", sep = "")),
                     minor_breaks = NULL) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_color_brewer(name = "Effect type", palette = "Dark2", 
                     breaks = c("Fisher's z", "MD", "SMD")) +
  theme(legend.position = c(0.8, 0.4),
        legend.background = element_rect(linetype = "solid", color = "black"))

>>>>

#combined line plot gives good overview.
ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type)) +
  geom_line(alpha = 0.6) +
  theme_bw() +
  scale_x_continuous(name = expression(paste("Between studies standard deviation ", tau)),
                     minor_breaks = NULL) +
  scale_y_continuous(name = expression(paste(I^2," index", sep = "")),
                     minor_breaks = NULL) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_color_brewer(name = "Effect type", palette = "Dark2", 
                     breaks = c("Fisher's z", "MD", "SMD")) +
  theme(legend.position = c(0.8, 0.4),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  guides(color = guide_legend(override.aes = list(size = 1.4)))
